Was Devon Allen Unjustly Disqualified at the 2022 World Track and Field Championships?

### 2023-02-14 Manuscript/manuscript.tex
Added table

>>>>

\section{Simulations}
\label{sec:simulation}

A simulation was performed on the gamma model with the year effect and link set
to "log". At a size of n=12,000,000, the calculated probability of a reaction
time being below 0.1 seconds was as follows for the various different data sets:

\begin{center}
  \begin{tabular}{||c|c||} 
   \hline
   Data Set & P RxnTime 0.1 \\ 
   \hline\hline
   all finals gamma log & 0.000856 \\ 
   \hline
   old finals gamma log & 0.000425 \\
   \hline
   all pooled gamma log & 0.00684 \\
   \hline
   old pooled gamma log & 0.00569 \\
  \end{tabular}
  \end{center}

Prior to the 2022 World Championship, there was a 0.0425\% chance (based on the
simulated results) of observing a reaction time below 0.01 seconds in the men's
finals.  That means that we would expect a time below the threshold to occur
once every 2,352 starts.  Considering there are roughly 8 men's finals reaction
times every 2 years (The World Championship is biennial), every 588 years there
should be a time as extreme as Allen's.  This seems extremely unlikely and thus
it seems like there may be an additonal explanantion for the fast reaction times.

If IAAF wanted the probability for a false start to be once every 100 years,
then they should change the false start barrier to
